Forecasting US Presidential Election Results Using Bayesian Prediction

### 2024-11-03 paper/paper_FV1.qmd
Add files via upload

This project is motivated and guided by Rohan Alexander and his book [@tellingstories]. Data used in this paper was downloaded, cleaned and analyzed with the programming language **R** [@citeR]. Also with support of additional packages in R: `ggplot2` [@citeGgplot2], `rstan`  [@citeRstan], `dplyr` [@citeDplyr], `here` [@citeHere], `knitr` [@citeKnitr].

>>>>

This project is motivated and guided by Rohan Alexander and his book [@tellingstories]. All the data used in this paper is derived from FiveThirtyEight’s U.S. [@FiveThirtyEight_Polls], and all the data analysis was done through the programming language **R** [@citeR]. Also with the support of additional packages in R: `ggplot2` [@citeGgplot2], `rstan`  [@citeRstan], `dplyr` [@citeDplyr], `here` [@citeHere], `knitr` [@citeKnitr].
